Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:预测人数和实际人数的关系，如果猜的准，应落在45°线上。通过两者关系图，可以看出一些猜和实际的规律。

***

### Scatterplots
Notes:注意qplot可以不用指定x、y，函数会自动按x第一、y第二识别。
散点图生成后，通常，最好想一下是什么产生了数据集中的某些怪现象或值。这能帮助我们解释脏数据。



```{r Scatterplots}
getwd()
dir()

library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

qplot(x = age, y = friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response:从图发现，年龄集中在30岁以下，好友人数集中在1000人以下甚至更少。

参考：年轻人的好友数会多达好几千人；有明显的虚假年龄。

***

### ggplot Syntax
Notes:qplot是快速绘图。ggplot是更正式的语法，主要的差别在于：一是需要指定geom或者图表类型；二是需要用aes包裹。
另外需要注意的是，可以通过“+”运算，来逐步增加图层并随时调整修改图像。


```{r ggplot Syntax}
qplot(x = age, y = friend_count, data = pf)
ggplot(aes(x = age, y = friend_count), data = pf) + geom_point() +
  xlim(13, 90)
summary(pf$age)
```

***

### Overplotting
Notes:重叠绘制的情况出现时，图像会看不清晰。这时，可以用α和geom来设置透明度解决。
继续用geom_jitter()可以增加抖动噪音，让重复的点分离开来。

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) + geom_jitter(alpha = 1/20) +
  xlim(13, 90)
```

#### What do you notice in the plot?
Response:1、好友人数呈现“增加-减少-增加-再减少”的趋势；
2、年轻人好友人数更多；
3、号称年龄70岁的人数比较多。

答案：年轻用户人数并没有想像的那么高，大概在1000以下；其次是69岁人数比较多。

***

### Coord_trans()
Notes:用coord_trans来调整坐标轴的显示。
运行代码 ?coord_trans 以查找有关 coord_trans() 的文档，或者访问 http://docs.ggplot2.org/current/coord_trans.html


```{r Coord_trans()}
d <- subset(pf, friend_count > 0)
ggplot(aes(x = age, y = friend_count), data = d) + 
  geom_jitter(alpha = 1/20) +
  xlim(13, 90) + 
  coord_trans(y = "sqrt")
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

由于抖动jitter会产生一些负数，可以考虑用position来处理。

如果是原本数据中的负数和0数据，经尝试可用subset来处理。


```{r}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) + 
  coord_trans(y = "sqrt")
```

#### What do you notice?
与之前相比，该图的变化趋势更明显。

***

### Alpha and Jitter
Notes:探索friends initiated 和 age的关系

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = 'sqrt')

```

***

### Overplotting and Domain Knowledge
Notes:
转换坐标轴，让数据更有意义
***

### Conditional Means
Notes:课程链接中有关于dplyr包的简介及教程等

常用的函数包括：filter()、group_by()、mutate()、arrange()

```{r Conditional Means}
library(dplyr)

age_group <- group_by(pf, age)
pf.fc_by_age = summarise(age_group,
          friend_count_mean = mean(friend_count),
          friend_coun_median = median(friend_count),
          n = n())

pf.fc_by_age <- arrange(pf.fc_by_age, age)

head(pf.fc_by_age)
```

上述代码的另一种写法
```{r}
pf.fc_by_age <- pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_coun_median = median(friend_count),
            n = n()) %>%
  arrange(age)
```


Create your plot!

```{r Conditional Means Plot}

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

